Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-05 Cover_letter_JPM.tex
finished

Dear Ms. Sonia Sun:

@@

We have since revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner,

%{% A SUMMARY
%=A summary modified/answers in cover letter (finish the first page) {
We re-wrote the Introduction with the studies of TCGA database according to the suggestion by reviewer\#2.
%[introduction] ok
%Answer 2-6 minor2 (how to study TCGA)
We introduced an independent HNSCC dataset (GSE65858) to provide more cases and evidence for supporting our biomarker candidates. The Results, Materials and Methods have included this information.
%[results] ok Answer 2-3 (GSE65858 then final 3 candidates)
We modified the Discussions about sample size, sliding window method, removal of "unclean data" statement according to the suggestion by reviewer\#2.
%[discussions] ok
%Answer 2-3 (sample size, effect size, pvalueTex cutoff of NDFIP1,  and P value)
%purpose of sliding window (ok 提 一下at  2-6 minor3)
%Answer 2-6 minor3 (In line 154 paragraph, what does "unclean data")
And the 'holistic cancer care" was also modified according to the suggestion by reviewer\#1.
%Answer 1-2 (holistic) figure 5
We added the description of FDR correction and Cox modeling in the Materials and Methods according to the suggestion by reviewer\#2.
%[materials and methods] ok
%Answer 2-1 (cutoff finding), replaced a new Figure 5 %(Figure_4_CAMK2N1_IL19_FCGBP.pdf)
%Answer 2-4 (Cox regression)
%Answer 2-3 (GSE65858)
%}
We modified Figure 1 and 2 according to the suggestion by reviewer\#2.
And new Figure 3, 4, 5 ,Table 1 and 2 was made for the updated results from GSE65858.
We also added new supplementary Figure S1.
%"Are the conclusions supported by the results?
%We provide more evidence by additional analysis of TCGA and GEO databases. %Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
%, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
%to provide more evidence from the significant literature review.
And all our responses to reviewers' comments are in the following pages.

%According to the editor's comments, we have the manuscript checked for English grammar. %
We wish our revised manuscript could be satisfied and accepted for publication in Journal of Personalized Medicine. 
Thanks very much for the kind helps and the reviewers' critical comments.
%\\[0.4cm]
Kind regards,

Yu-Chuan (Jack) Li, M.D., Ph.D.

Graduate Institute of Biomedical Informatics, 
College of Medical Science and Technology,\\
Taipei Medical University,
Taipei, Taiwan

>>>>

Dear Ms. Sonia Sun:\\[0.3cm]

@@

We have since revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner.

%{% A SUMMARY
%=A summary modified/answers in cover letter (finish the first page) {
We re-wrote the Introduction with the studies of TCGA database according to the suggestion by reviewer\#2.
%[introduction] ok
%Answer 2-6 minor2 (how to study TCGA)
We introduced an independent HNSCC dataset (GSE65858) to provide more cases and evidence for supporting our biomarker candidates. The Results, Materials and Methods have included this information.
%[results] ok Answer 2-3 (GSE65858 then final 3 candidates)
We modified the Discussions about sample size, sliding window method, and removal of "unclean data" statement according to the suggestion by reviewer\#2.
%[discussions] ok
%Answer 2-3 (sample size, effect size, pvalueTex cutoff of NDFIP1,  and P value)
%purpose of sliding window (ok 提 一下at  2-6 minor3)
%Answer 2-6 minor3 (In line 154 paragraph, what does "unclean data")
And the 'holistic cancer care" was also modified according to the suggestion by reviewer\#1.
%Answer 1-2 (holistic) figure 5
We added the description of FDR correction and Cox modeling in the Materials and Methods according to the suggestion by reviewer\#2.
%[materials and methods] ok
%Answer 2-1 (cutoff finding), replaced a new Figure 5 %(Figure_4_CAMK2N1_IL19_FCGBP.pdf)
%Answer 2-4 (Cox regression)
%Answer 2-3 (GSE65858)
%}
We modified Figure 1 and 2 according to the suggestion by reviewer\#2.
And new Figure 3, 4, 5, Table 1 and 2 was made for the updated results from GSE65858.
We also added new supplementary Figure S1.
%"Are the conclusions supported by the results?
%We provide more evidence by additional analysis of TCGA and GEO databases. %Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
%, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
%to provide more evidence from the significant literature review.
And all our responses to reviewers' comments are in the following pages.

%According to the editor's comments, we have the manuscript checked for English grammar. %
We wish our revised manuscript could be satisfied and accepted for publication in Journal of Personalized Medicine. 
Thank you very much for the kind helps and the reviewers' critical comments.\\[0.3cm]

Kind regards,\\[0.1cm]
Yu-Chuan (Jack) Li, M.D., Ph.D.\\
Graduate Institute of Biomedical Informatics, 
College of Medical Science and Technology,\\
Taipei Medical University,
Taipei, Taiwan
